{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-31 Paper/main.tex
Some estimation theory

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ of the following equation.

@@

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi_j(\omega) = \langle X(\omega) - \mu, \nu_j\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu_j(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector. {\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}

@@

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}x_j(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(x_j(t) - \hat{\mu}(t)\right) \left(x_j(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathbb{N}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathbb{N}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathbb{N}$.}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
	\end{equation}

@@

	\subsection{Estimation using Basis-Representation}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.

@@

	{\color{red} This fancy equation will be very useful to explain our simulation.}

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega) 
			= \alpha + \sum_{j \in \mathcal{I}} \left[ b_j \sum_{k \in \mathcal{L}} \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[b_j {\color{violet}\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega) 
			= \alpha + \sum_{j = 1}^{J} b_j {\color{violet}\tilde{Z}_j(\omega)} + \epsilon(\omega) 
		\end{split}
	\end{equation}

	A typical choice in this scenario is to use the same functional basis and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations. This leads to the following simplification of Equation \ref{basis_exp_transf}.

	\begin{equation}
		\begin{split}
			Z_{j, k}(\omega) & = d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \quad j = 1, \dots, L \quad k = 1, \dots, L \\
			\tilde{Z}_j(\omega) & = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
		\end{split}
	\end{equation}

	\subsection{Estimation using Functional Principal Components}

	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( f_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]
			\approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
		\end{split}
	\end{equation}

	Again using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.

>>>>

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda^m, \nu^m) \: \vert \: m \in \mathbb{N}\}$ of the following equation.

@@

	The $\xi_j(\omega)$ are then given as 
	\begin{equation}
		\xi^m(\omega) = \langle X(\omega) - \mu, \nu^m\rangle = \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation} 
	and thereby random variables realizing in $\mathbb{R}$ and have the following properties akin to $\Lambda^{\frac{1}{2}} D(\omega)$ for the case of a random vector. {\color{orange} We would need to assume that the process is centered, otherwise we may not derive below results(not sure though).}

@@

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{i = 1}^{n}x_i(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{i = 1}^{n} \left(x_i(t) - \hat{\mu}(t)\right) \left(x_i(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}^m, \hat{\nu}^m) \: \vert \: m \in \mathcal{M}\}$ for $\{(\lambda^m, \nu^m) \: \vert \: i \in \mathcal{M}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathcal{M}$.}

@@

	\begin{equation}
		x_i(t) = \hat{\mu}(t) + \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
	\end{equation}
	where the $\hat{\xi}_{i}^m$ are derived as

	\begin{equation}
		\hat{\xi}_i^m(\omega) = \langle x_i - \hat{\mu}, \hat{\nu}^m\rangle = \int_{0}^{1} \left(x_i(s) - \hat{\mu}(s)\right) \hat{\nu}^m(s) \mathrm{d}s
	\end{equation}

	In reality these calculations are often done using basis representations of both the functional principal components $\hat{\nu}^m$ and the observations $x_i(t)$ leading to the following representation.

	\begin{equation}\label{FPCA_basis_expansion}
		\begin{split}
			\hat{\xi}_{i}^m & = \int_{0}^{1} {\color{red}\left( x_i(s) - \hat{\mu}(s)\right)} {\color{blue}\hat{\nu}^m(s)} \mathrm{d}s
			= \int_{0}^{1} {\color{red}\left(\sum_{j \in \mathcal{I}} a_{i,j} \phi_j(s)\right)} {\color{blue}\left(\sum_{k \in \mathcal{L}} b_{k}^m \psi_{k}(s)\right)} \mathrm{d}s \\
			& = \sum_{j \in \mathcal{I}} \left[ a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal}  b_{k}^m \int_{0}^{1} \phi_j(s) \psi_{k}(s)\mathrm{d}s}\right]
			= \sum_{j \in \mathcal{I}} \left[a_{i,j}\sum_{k \in \mathcal{L}} {\color{teal} Z_{j,k}^m} \right]\\
			& \approx \sum_{j = 1}^{J} \left[a_{i,j}{\color{violet}\sum_{k = 1}^{K} Z_{j,k}^m} \right]
			= \sum_{j = 1}^{J} a_{i,j}{\color{violet}\tilde{Z}_{j}^m}
		\end{split}
	\end{equation}

	Using the same basis and the same truncation parameter $L$ leads to the following simplifications of Equation \ref{FPCA_basis_expansion}.

	For notational purposes in this paper we define the following convention:

	\begin{equation}
		\tilde{\xi}^{m,L}_{i} = \sum_{j = 1}^{L} \left[ a_{i,j}\sum_{k = 1}^{L} b_{k}^m \int_{0}^{1} \phi_j(s) \phi_{k}(s)\mathrm{d}s\right]
	\end{equation}

@@

	\subsubsection{Estimation using Basis-Representation}
	The most common way to make this problem tractable is via a basis representation of $\beta(t)$. Therefore, let $\{b_i(t) \: \vert \: i \in \mathbb{N}\}$ be a basis of $\mathbb{L}^2[0,1]$ and represent $\beta(t)$ in terms of this basis.

@@

	In practice it is common to not only express the coefficient function in terms of a basis but also the observations. Therefore two bases ($\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and $\left(\psi_k(t)\right)_{k \in \mathcal{L}}$) and two corresponding truncation parameters ($J$ and $K$) can be chosen. This leads to the following representation.

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega)
			 = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} b_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} b_j \left[\sum_{k \in \mathcal{L}} d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega) 
			\approx \alpha + \sum_{j = 1}^{J} \left[b_j \sum_{k = 1}^{K}  d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s\right] + \epsilon(\omega)
		\end{split}
	\end{equation}

	A typical choice in this scenario is to use the same functional basis $\left(\phi_j(t)\right)_{j \in \mathcal{I}}$ and the same truncation parameter $L$ for both the coefficient function and the approximation of the observations. Defining the following notation

	\begin{equation}
			\tilde{Z}_j(\omega) = \sum_{k = 1}^{L} \left[d_k(\omega) \int_{0}^{1} \phi_j(s) \phi_k(s) \mathrm{d}s \right] \quad j = 1, \dots, L
	\end{equation}

	This leads to a considerable simplification of Equation \ref{basis_exp_transf}.

	\begin{equation}\label{simplified_model_basis_equation}
		Y(\omega) \approx \alpha + \sum_{j = 1}^{J} b_j \tilde{Z}_j(\omega) + \epsilon(\omega)
	\end{equation}

	A model in the form of Equation \ref{simplified_model_basis_equation} lends itself to be estimated using theory from multivariate linear regression.

	\subsubsection{Estimation using Functional Principal Components}

	% maybe use n for coefficents in expansion of nu? before b for beta, so this could be a consistent choice
